What is an Ancestral Recombination Graph?

### 2022-01-10 paper.tex
Add initial ASG refs

\section*{The ARG as a stochastic process}
The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

We suggest that the process definition should be called the "coalescent with recombination" (CwR), reserving the term ARG to refer to the graph structure itself.

>>>>

\section*{Ancestral graphs and stochastic processes}
The coalescent
process~\citep{kingman1982coalescent,kingman1982genealogy,hudson1983testing,
tajima1983evolutionary}

@@

In the theoretical literature, ancestral graphs such as the ARG refer to the
ancestral \emph{process} rather than the outcome of a process.
For example, the Ancestral Selection
Graph~\citep{krone1997ancestral,neuhauser1999ancestral} models selection
as a graph with virtual lineages [etc etc.]. Importantly, the graph structure
of the ASG does \emph{not} correspond to a realised ancestry, but rather
models possible outcomes.
